Quasi-universal acceptance of basic science in the US

### 2024-09-19 appendix_exp1.Rmd
make WORD compatible tables for PUS submission

# # Create the table
kbl(conspiracy_measures, booktabs = T, longtable = T,
    caption = "Conspiracy measures", full_width = T) %>%
  kable_styling(font_size = 8) %>% 
  column_spec(1, width = "10em") %>%
  column_spec(2, width = "20em") %>%
  column_spec(3, width = "10em")

# Use apa_table to format the table
# apa_table(
#   conspiracy_measures,
#   caption = "Overview of Conspiracy Thinking Measures",
#   align = c("m{4cm}", "m{10cm}", "m{4cm}")
# )
```

@@

kbl(table, booktabs = T, longtable = TRUE,
    caption = "Comments of participants on Study 1") %>%
  kable_paper(full_width = F) %>% 
  column_spec(1) %>%
  column_spec(2, width = "40em") 
```

>>>>

# Create the basic table
if (knitr::is_latex_output() || knitr::is_html_output()) {
  # For LaTeX or HTML: Use kbl, column_spec, and kable_styling
  table_output <- conspiracy_measures %>%
    kbl(
      booktabs = TRUE, 
      longtable = TRUE,
      caption = "Conspiracy measures",
      full_width = TRUE
    ) %>%
    kableExtra::kable_styling(font_size = 8) %>%
    kableExtra::column_spec(1, width = "10em") %>%
    kableExtra::column_spec(2, width = "20em") %>%
    kableExtra::column_spec(3, width = "10em")
} else {
  # For Word: Use flextable for better Word compatibility
  table_output <- flextable::flextable(conspiracy_measures) %>%
    flextable::set_caption(caption = "Conspiracy measures") %>%
    flextable::autofit() %>%
    flextable::width(j = 1, width = 2) %>%
    flextable::width(j = 2, width = 4) %>%
    flextable::width(j = 3, width = 2) # Adjust widths as needed
}

# Display the table
table_output
```

@@

# Create the basic table
if (knitr::is_latex_output() || knitr::is_html_output()) {
  # For LaTeX or HTML: Use kbl, column_spec, and kable_paper
  table_output <- table %>%
    kbl(
      booktabs = TRUE, 
      longtable = TRUE,
      caption = "Comments of participants on Study 1"
    ) %>%
    kableExtra::kable_paper(full_width = FALSE) %>%
    kableExtra::column_spec(1) %>%
    kableExtra::column_spec(2, width = "40em")
} else {
  # For Word: Use flextable for better Word compatibility
  table_output <- flextable::flextable(table) %>%
    flextable::set_caption(caption = "Comments of participants on Study 1") %>%
    flextable::autofit() %>%
    flextable::width(j = 2, width = 4.5) # Adjust column widths as needed
}

# Display the table
table_output
```

### 2024-09-19 appendix_exp2.Rmd
make WORD compatible tables for PUS submission

kbl(table, booktabs = T, longtable = TRUE,
    caption = "Reasons for consensus rejection (raw answers)") %>%
  kable_paper(full_width = F) %>% 
  column_spec(1) %>%
  column_spec(2) %>%
  column_spec(3, width = "30em")

>>>>

# Create the basic table
if (knitr::is_latex_output() || knitr::is_html_output()) {
  # For LaTeX or HTML: Use kbl, column_spec, and kable_paper
  table_output <- table %>%
    kbl(
      booktabs = TRUE, 
      longtable = TRUE,
      caption = "Reasons for consensus rejection (raw answers)"
    ) %>%
    kableExtra::kable_paper(full_width = FALSE) %>%
    kableExtra::column_spec(1) %>%
    kableExtra::column_spec(2) %>%
    kableExtra::column_spec(3, width = "30em")
} else {
  # For Word: Use flextable for better Word compatibility
  table_output <- flextable::flextable(table) %>%
    flextable::set_caption(caption = "Reasons for consensus rejection (raw answers)") %>%
    flextable::autofit() %>%
    flextable::width(j = 3, width = 4.5) # Adjust column width for the third column
}

# Display the table
table_output
```

### 2024-09-19 appendix_exp3.Rmd
make WORD compatible tables for PUS submission

# Output the table
kbl(items, booktabs = T, longtable = TRUE,
    caption = "Science knowledge items", 
    full_width = T) %>%
  kable_styling(font_size = 8) %>% 
  column_spec(1, width = "1em") %>%
  column_spec(2, width = "10em") %>%
  column_spec(3, width = "10em") %>%
  column_spec(4, width = "23em") 
```

@@

# apa_table(table,
#           align = c("m{1cm}", "m{3cm}", "m{10cm}"), 
#           longtable = TRUE
#           )
kbl(table, booktabs = T, longtable = TRUE,
    caption = "Reasons for consensus rejection (raw answers)") %>%
  kable_paper(full_width = F) %>% 
  column_spec(1) %>%
  column_spec(2) %>%
  column_spec(3, width = "30em")

@@

kbl(table, booktabs = T, longtable = TRUE,
    caption = "Reasons for consensus acceptance (participants who answered 'other')") %>%
  kable_paper(full_width = F) %>% 
  column_spec(1) %>%
  column_spec(2, width = "30em")
```

@@

kbl(table, booktabs = T, longtable = TRUE,
    caption = "Answers from participants saying they trusted the scientific consens because they verified independently on how they did so.") %>%
  kable_paper(full_width = F) %>% 
  column_spec(1) %>%
  column_spec(2, width = "30em")
```

>>>>

# Create the basic table
if (knitr::is_latex_output() || knitr::is_html_output()) {
  # For LaTeX or HTML: Use kbl, column_spec, and kable_styling
  table_output <- items %>%
    kbl(
      booktabs = TRUE, 
      longtable = TRUE,
      caption = "Science knowledge items", 
      full_width = TRUE
    ) %>%
    kableExtra::kable_styling(font_size = 8) %>%
    kableExtra::column_spec(1, width = "1em") %>%
    kableExtra::column_spec(2, width = "10em") %>%
    kableExtra::column_spec(3, width = "10em") %>%
    kableExtra::column_spec(4, width = "23em")
} else {
  # For Word: Use flextable for better Word compatibility
  table_output <- flextable::flextable(items) %>%
    flextable::set_caption(caption = "Science knowledge items") %>%
    flextable::autofit() %>%
    flextable::width(j = 1, width = 0.8) %>%
    flextable::width(j = 2, width = 3) %>%
    flextable::width(j = 3, width = 3) %>%
    flextable::width(j = 4, width = 6) # Adjust column widths as needed
}

# Display the table
table_output
```

@@

# Create the basic table
if (knitr::is_latex_output() || knitr::is_html_output()) {
  # For LaTeX or HTML: Use kbl, column_spec, and kable_paper
  table_output <- table %>%
    kbl(
      booktabs = TRUE, 
      longtable = TRUE,
      caption = "Reasons for consensus rejection (raw answers)"
    ) %>%
    kableExtra::kable_paper(full_width = FALSE) %>%
    kableExtra::column_spec(1) %>%
    kableExtra::column_spec(2) %>%
    kableExtra::column_spec(3, width = "30em")
} else {
  # For Word: Use flextable for better Word compatibility
  table_output <- flextable::flextable(table) %>%
    flextable::set_caption(caption = "Reasons for consensus rejection (raw answers)") %>%
    flextable::autofit() %>%
    flextable::width(j = 3, width = 4.5) # Adjust column width for the third column
}

# Display the table
table_output

@@

# Create the basic table
if (knitr::is_latex_output() || knitr::is_html_output()) {
  # For LaTeX or HTML: Use kbl, column_spec, and kable_paper
  table_output <- table %>%
    kbl(
      booktabs = TRUE, 
      longtable = TRUE,
      caption = "Reasons for consensus acceptance (participants who answered 'other')"
    ) %>%
    kableExtra::kable_paper(full_width = FALSE) %>%
    kableExtra::column_spec(1) %>%
    kableExtra::column_spec(2, width = "30em")
} else {
  # For Word: Use flextable for better Word compatibility
  table_output <- flextable::flextable(table) %>%
    flextable::set_caption(caption = "Reasons for consensus acceptance (participants who answered 'other')") %>%
    flextable::autofit() %>%
    flextable::width(j = 2, width = 4.5) # Adjust column width for the second column
}

# Display the table
table_output
```

@@

# Create the basic table
if (knitr::is_latex_output() || knitr::is_html_output()) {
  # For LaTeX or HTML: Use kbl, column_spec, and kable_paper
  table_output <- table %>%
    kbl(
      booktabs = TRUE, 
      longtable = TRUE,
      caption = "Answers from participants saying they trusted the scientific consensus because they verified independently on how they did so."
    ) %>%
    kableExtra::kable_paper(full_width = FALSE) %>%
    kableExtra::column_spec(1) %>%
    kableExtra::column_spec(2, width = "30em")
} else {
  # For Word: Use flextable for better Word compatibility
  table_output <- flextable::flextable(table) %>%
    flextable::set_caption(caption = "Answers from participants saying they trusted the scientific consensus because they verified independently on how they did so.") %>%
    flextable::autofit() %>%
    flextable::width(j = 2, width = 4.5) # Adjust column width for the second column
}

# Display the table
table_output
```

### 2024-09-19 appendix_exp4.Rmd
make WORD compatible tables for PUS submission

# Output the table
kbl(items_cleaned, booktabs = T, longtable = TRUE,
    caption = "Science knowledge items", full_width = T) %>%
  kable_styling(font_size = 8) %>%
  column_spec(1, width = "1em") %>%
  column_spec(2, width = "12em") %>%
  column_spec(3, width = "10em") %>%
  column_spec(4, width = "12em")
```

@@

# apa_table(table,
#           align = c("m{1cm}", "m{3cm}", "m{10cm}"), 
#           longtable = TRUE
#           )
kbl(table, booktabs = T, longtable = TRUE,
    caption = "Reasons for consensus rejection (raw answers)") %>%
  kable_paper(full_width = F) %>% 
  column_spec(1) %>%
  column_spec(2) %>%
  column_spec(3, width = "30em")

```

>>>>

# Create the basic table
if (knitr::is_latex_output() || knitr::is_html_output()) {
  # For LaTeX or HTML: Use kbl, column_spec, and kable_styling
  table_output <- items_cleaned %>%
    kbl(
      booktabs = TRUE, 
      longtable = TRUE,
      caption = "Science knowledge items", 
      full_width = TRUE
    ) %>%
    kableExtra::kable_styling(font_size = 8) %>%
    kableExtra::column_spec(1, width = "1em") %>%
    kableExtra::column_spec(2, width = "12em") %>%
    kableExtra::column_spec(3, width = "10em") %>%
    kableExtra::column_spec(4, width = "12em")
} else {
 # For Word: Use apa_table for better Word compatibility
  table_output <- papaja::apa_table(
    items_cleaned, 
    caption = "Science knowledge items"
  )
}

# Display the table
table_output
```

@@

# Create the basic table
if (knitr::is_latex_output() || knitr::is_html_output()) {
  # For LaTeX or HTML: Use kbl, column_spec, and kable_paper
  table_output <- table %>%
    kbl(
      booktabs = TRUE, 
      longtable = TRUE,
      caption = "Reasons for consensus rejection (raw answers)"
    ) %>%
    kableExtra::kable_paper(full_width = FALSE) %>%
    kableExtra::column_spec(1) %>%
    kableExtra::column_spec(2) %>%
    kableExtra::column_spec(3, width = "30em")
} else {
  # For Word: Use flextable for better Word compatibility
  table_output <- flextable::flextable(table) %>%
    flextable::set_caption(caption = "Reasons for consensus rejection (raw answers)") %>%
    flextable::autofit() %>%
    flextable::width(j = 3, width = 4.5) # Adjust column width for the third column
}

# Display the table
table_output
```

### 2024-09-19 paper.Rmd
make WORD compatible tables for PUS submission

# Output the table
knitr::kable(items_cleaned, booktabs = T, longtable = TRUE,
    caption = "Science knowledge items", 
    full_width = T, 
    col.names = c("", "Study 1-3", "Study 4")) %>%
  kable_styling(font_size = 8) %>%
  column_spec(1, width = "2em") %>%
  column_spec(2, width = "22em")%>%
  column_spec(3, width = "22em") %>% 
  footnote(symbol = "Only used in Study 1")
```

@@

# Output the table
kbl(conspiracy_items, booktabs = T, longtable = T, col.names = NULL,
    caption = "Conspiracy items", full_width = T) %>%
  kable_styling(font_size = 8) %>% 
  column_spec(1, width = "3em") %>%
  column_spec(2, width = "40em") %>% 
  footnote(general = "Participants were asked to rate their belief in the conspiracy on a scale from 1 to 9, with the labels: `1 - completely false, 5 - unsure, 9 - completely true`.",
           escape = FALSE,
           footnote_as_chunk = TRUE,
           threeparttable = TRUE)
```

>>>>

# Output the table
# Create the basic table
if (knitr::is_latex_output() || knitr::is_html_output()) {
  # For LaTeX or HTML: Use kable, column_spec, and kable_styling
  table_output <- items_cleaned %>%
    knitr::kable(
      booktabs = TRUE, 
      longtable = TRUE,
      caption = "Science knowledge items",
      full_width = TRUE,
      col.names = c("", "Study 1-3", "Study 4")
    ) %>%
    kableExtra::kable_styling(font_size = 8) %>%
    kableExtra::column_spec(1, width = "2em") %>%
    kableExtra::column_spec(2, width = "22em") %>%
    kableExtra::column_spec(3, width = "22em") %>%
    kableExtra::footnote(
      symbol = "Only used in Study 1"
    )
} else {
  # For Word: Use apa_table
  table_output <- papaja::apa_table(
    items_cleaned, 
    caption = "Science knowledge items",
    note = "*Only used in Study 1",
    col.names = c("", "Study 1-3", "Study 4")
    #,align = c("l", "m{8cm}", "m{8cm}")
  )
}

# Display the table
table_output

@@

# Create the basic table
if (knitr::is_latex_output() || knitr::is_html_output()) {
  # For LaTeX or HTML: Use kbl, column_spec, and kable_styling
  table_output <- conspiracy_items %>%
    kbl(
      booktabs = TRUE, 
      longtable = TRUE,
      col.names = NULL,
      caption = "Conspiracy items",
      full_width = TRUE
    ) %>%
    kableExtra::kable_styling(font_size = 8) %>%
    kableExtra::column_spec(1, width = "3em") %>%
    kableExtra::column_spec(2, width = "40em") %>%
    kableExtra::footnote(
      general = "Participants were asked to rate their belief in the conspiracy on a scale from 1 to 9, with the labels: `1 - completely false, 5 - unsure, 9 - completely true`.",
      escape = FALSE,
      footnote_as_chunk = TRUE,
      threeparttable = TRUE
    )
} else {
  # For Word: Use apa_table
  table_output <- papaja::apa_table(
    conspiracy_items, 
    caption = "Conspiracy items",
    note = "Participants were asked to rate their belief in the conspiracy on a scale from 1 to 9, with the labels: `1 - completely false, 5 - unsure, 9 - completely true`.",
    col.names = c("", "") # Replace with specific column names if desired
  )
}

# Display the table
table_output
```

### 2024-09-19 paper.tex
make WORD compatible tables for PUS submission

\begin{longtable}[t]{>{\raggedleft\arraybackslash}p{2em}>{\raggedright\arraybackslash}p{22em}>{\raggedright\arraybackslash}p{22em}}
\caption{\label{tab:knowledge}Science knowledge items}\\
\toprule
 & Study 1-3 & Study 4\\
\midrule
1 & Do antibiotics kill viruses as well as bacteria? [Yes, both; No, only viruses; No, only bacteria] & For which disease is the drug bedaquiline, developed in 2007, a treatment? [Tetanus; Tuberculosis; Malaria]\\
2 & Are electrons smaller, larger, or the same size as atoms? [Smaller; Same size; Larger] & What is the maximum speed a proton can attain in the largest particle collider as to 2015? [90\% of the speed of light; 99\% of the speed of light; the speed of light]\\
3 & Have the continents on Earth been moving for millions of years or have they always been where they are now? [They have been moving; They have always been where they are now] & Kepler-452b is an exoplanet revolving around the star Kepler-452. How far away from the star is it, as established by astronomers in 2015? [97 million mi; 1,2 million mi; 1254 million mi]\\
4 & What decides whether a baby is a boy or a girl ? Is it the father's genes, the mother's genes, or both? [The mother's genes; the father's genes; both] & Using bomb-pusle dating with carbon 14, what is the age of the oldest known vertebrate, as established in 2016? [138 years; 205 years;  392 years]\\
5 & Do lasers work by focusing sound waves? [Yes; No] & How many more glial cells are there in the brain in comparison with neurons, as established in 2016? [The same amount; Twice as many; Ten times as many]\\
\addlinespace
6 & How long does it take for Earth to go around the sun: one day, one month, or one year? [One day; One month; One year] & As predicted by the general theory of relativity, how many times would the Earth keep orbiting if the Sun disappeared, as established in 2012? [47 seconds; 8 minutes;  2 hours]\\
7 & Are diamonds made of carbon? [Yes; No] & What is the electric charge of the Higgs Boson, as established in 2012? [1.602176634 x 10-19; 0; 3.2x10-19C]\\
8 & Which travels faster : light or sound? [Light; Sound] & What is the age of the oldest materials formed on Earth, as established in 2020? [Less than 4.6 Ga; Around 4.6 Ga; More than 4.6 Ga]\\
9 & Is common table salt made of calcium carbonate? [Yes; No] & With the best current cloning techniques, what is the average success rate when operated on mice, as of 2010? [2,7\%; 9,4\%; 17,2\%]\\
10 & Is water made of molecules containing one oxygen and two hydrogen atoms? [Yes; No] & What was the strength of the Earth magnetic field 3.7 billion years ago, as discovered this year? [15 microtesla; 30 microtesla; 45 microtesla]\\
\addlinespace
11 & *Where do trees mainly draw the materials with which they create their mass? [Earth; Water; Air] & \\
\bottomrule
\multicolumn{3}{l}{\rule{0pt}{1em}\textsuperscript{*} Only used in Study 1}\\
\end{longtable}
\endgroup{}

@@

\begin{ThreePartTable}
\begin{TableNotes}[para]
\item \textit{Note: } 
\item Participants were asked to rate their belief in the conspiracy on a scale from 1 to 9, with the labels: `1 - completely false, 5 - unsure, 9 - completely true`.
\end{TableNotes}
\begin{longtable}[t]{>{\raggedleft\arraybackslash}p{3em}>{\raggedright\arraybackslash}p{40em}}
\caption{\label{tab:conspiracy}Conspiracy items}\\
\toprule
1 & The Apollo moon landings never happened and were staged in a Hollywood film studio.\\
2 & A cure for cancer was discovered years ago, but this has been suppressed by the pharmaceutical industry and the U.S. Food and Drug Administration (FDA).\\
3 & The spread of certain viruses and/or diseases is the result of the deliberate, concealed efforts of vested interests.\\
4 & The claim that the climate is changing due to emissions from fossil fuels is a hoax perpetrated by corrupt scientists who want to spend more taxpayer money on climate research.\\
5 & The Earth is flat (not spherical) and this fact has been covered up by scientists and vested interests.\\
\addlinespace
6 & There is a causal link between vaccination and autism that has been covered up by the pharmaceutical industry.\\
7 & In the 1950s and 1960s more than 100 million Americans received a polio vaccine contaminated with a potentially cancer-causing virus.\\
8 & Proof of alien contact is being concealed from the public.\\
9 & Hydroxychloroquine has been demonstrated to be a safe and effective treatment of COVID and this information is being suppressed.\\
10 & Dinosaurs never existed, evolution is not real, and scientists have been faking the fossil record.\\
\bottomrule
\insertTableNotes
\end{longtable}
\end{ThreePartTable}
\endgroup{}

>>>>

\caption{\label{tab:knowledge}Science knowledge items}

\begin{tabular}{m{0.5cm}m{8cm}m{8cm}}
\toprule
 & Study 1-3 & Study 4\\
\midrule
1 & Do antibiotics kill viruses as well as bacteria? [Yes, both; No, only viruses; No, only bacteria] & For which disease is the drug bedaquiline, developed in 2007, a treatment? [Tetanus; Tuberculosis; Malaria]\\
2 & Are electrons smaller, larger, or the same size as atoms? [Smaller; Same size; Larger] & What is the maximum speed a proton can attain in the largest particle collider as to 2015? [90\% of the speed of light; 99\% of the speed of light; the speed of light]\\
3 & Have the continents on Earth been moving for millions of years or have they always been where they are now? [They have been moving; They have always been where they are now] & Kepler-452b is an exoplanet revolving around the star Kepler-452. How far away from the star is it, as established by astronomers in 2015? [97 million mi; 1,2 million mi; 1254 million mi]\\
4 & What decides whether a baby is a boy or a girl ? Is it the father's genes, the mother's genes, or both? [The mother's genes; the father's genes; both] & Using bomb-pusle dating with carbon 14, what is the age of the oldest known vertebrate, as established in 2016? [138 years; 205 years;\ \ 392 years]\\
5 & Do lasers work by focusing sound waves? [Yes; No] & How many more glial cells are there in the brain in comparison with neurons, as established in 2016? [The same amount; Twice as many; Ten times as many]\\
6 & How long does it take for Earth to go around the sun: one day, one month, or one year? [One day; One month; One year] & As predicted by the general theory of relativity, how many times would the Earth keep orbiting if the Sun disappeared, as established in 2012? [47 seconds; 8 minutes;\ \ 2 hours]\\
7 & Are diamonds made of carbon? [Yes; No] & What is the electric charge of the Higgs Boson, as established in 2012? [1.602176634 x 10-19; 0; 3.2x10-19C]\\
8 & Which travels faster : light or sound? [Light; Sound] & What is the age of the oldest materials formed on Earth, as established in 2020? [Less than 4.6 Ga; Around 4.6 Ga; More than 4.6 Ga]\\
9 & Is common table salt made of calcium carbonate? [Yes; No] & With the best current cloning techniques, what is the average success rate when operated on mice, as of 2010? [2,7\%; 9,4\%; 17,2\%]\\
10 & Is water made of molecules containing one oxygen and two hydrogen atoms? [Yes; No] & What was the strength of the Earth magnetic field 3.7 billion years ago, as discovered this year? [15 microtesla; 30 microtesla; 45 microtesla]\\
11 & *Where do trees mainly draw the materials with which they create their mass? [Earth; Water; Air] & NA\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} *Only used in Study 1}
\end{tablenotes}

@@

\caption{\label{tab:conspiracy}Conspiracy items}

\begin{tabular}{lp{10cm}}
\toprule
 & \\
\midrule
1 & The Apollo moon landings never happened and were staged in a Hollywood film studio.\\
2 & A cure for cancer was discovered years ago, but this has been suppressed by the pharmaceutical industry and the U.S. Food and Drug Administration (FDA).\\
3 & The spread of certain viruses and/or diseases is the result of the deliberate, concealed efforts of vested interests.\\
4 & The claim that the climate is changing due to emissions from fossil fuels is a hoax perpetrated by corrupt scientists who want to spend more taxpayer money on climate research.\\
5 & The Earth is flat (not spherical) and this fact has been covered up by scientists and vested interests.\\
6 & There is a causal link between vaccination and autism that has been covered up by the pharmaceutical industry.\\
7 & In the 1950s and 1960s more than 100 million Americans received a polio vaccine contaminated with a potentially cancer-causing virus.\\
8 & Proof of alien contact is being concealed from the public.\\
9 & Hydroxychloroquine has been demonstrated to be a safe and effective treatment of COVID and this information is being suppressed.\\
10 & Dinosaurs never existed, evolution is not real, and scientists have been faking the fossil record.\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} Participants were asked to rate their belief in the conspiracy on a scale from 1 to 9, with the labels: `1 - completely false, 5 - unsure, 9 - completely true`.}
\end{tablenotes}
